European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 manuscript/dissertation.qmd
share csl and bib (#5)

---
title: European or American? A re-examination of the transatlantic influence over the IMF
subtitle: GV499 Dissertation
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true

format:
  #native: default
  #docx: default
  orcid-pdf:
    keep-tex: true
    number-sections: true
bibliography: references.bib
csl: extra/apa.csl
abstract: This is an abstract.
keywords: IMF, US hegemony, Europe
---

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
# subtitle: GV499 Dissertation
date: last-modified
authors:
  - name: Dianyi Yang
    email: d.yang17@lse.ac.uk
    orcid: 0009-0004-4652-3429
    correspondence: true
format:
  #native: default
  #docx: default
  orcid-pdf:
    keep-tex: true
    number-sections: true
abstract: This is an abstract.
keywords: IMF, US hegemony, Europe
---
